Risk Perceptions for Wearable Devices

### 2015-03-07 tex-inputs/appendixes.tex
small adjust
final version

\section{Coding Label Definitions}
\label{sec:coding}
Researchers coded the self reported answers in the following way.\\

{\bf Privacy}: ``privacy,'' mention of personal details, spying. \\
{\bf Security}:  ``security,'' mention of malware, hacking. \\
{\bf GPS tracking}: ``location,'' ``GPS,'' mention of monitoring. \\
{\bf Being Unaware}: mention of using, collecting, and disclosing data without permission or in a different way than understood by user. \\
{\bf False information}: inaccurate or maliciously false data.\\
{\bf Health Risk}: mention of radiation, cancer, or health effects.\\
{\bf Safety}: mention of distractions causing car crashes or injuries, mugging or violence because of the device, injuries from device malfunctions (battery burns).\\
{\bf Discomfort}: mention of eye strain, headache, obscured vision, irritation. \\
{\bf Financial cost}: mention of getting ripped off by buying the device or device accessories, having to buy another device when broken or stolen, financial compromise caused by device. \\
{\bf Theft}: mention of device theft. \\
{\bf Social Impact}: mention of dependency, distance from friends and family, changes in decision making, social changes, etc. \\
{\bf Social Stigma}: mention of judgment, hate, or bystanders.\\ 
{\bf Aesthetics}: mention of fashion, the device being ugly, looking dorky. \\
{\bf Miscellaneous}: odd comments, uncommon concerns. \\
{\bf None}: ``None,'' mention of no threat, or no real concerns \\
{\bf Don't know}: ``do not know,'' general confusion \\
{\bf Don't care}: `` do not care,'' nonchalant answers

>>>>

\section{Coding Label Definitions}
\label{sec:coding}
Researchers coded the self reported answers as follows:\\
{\bf Privacy}: ``privacy,'' mention of personal details, spying. \\
{\bf Security}:  ``security,'' mention of malware, hacking. \\
{\bf GPS tracking}: ``location,'' ``GPS,'' mention of monitoring. \\
{\bf Being Unaware}: mention of using, collecting, and disclosing data without permission. \\
{\bf False information}: inaccurate or maliciously false data.\\
{\bf Health Risk}: mention of radiation, cancer, or other effects.\\
{\bf Safety}: mention of distractions causing car crashes and injuries, violence due to the device, injuries from malfunctions.\\
{\bf Discomfort}: mention of eye strain, headache, irritation. \\
{\bf Financial cost}: cost of buying or using the device. \\
{\bf Theft}: mention of device theft. \\
{\bf Social Impact}: mention of dependency, distance from people, changes in decision making, etc. \\
{\bf Social Stigma}: mention of judgment, hate, or bystanders.\\ 
{\bf Aesthetics}: mention of fashion or looking dorky. \\
{\bf Miscellaneous}: odd comments, uncommon concerns. \\
{\bf None}: ``None,'' mention of no threat, or no real concerns \\
{\bf Don't know}: ``do not know,'' general confusion \\
{\bf Don't care}: `` do not care,'' nonchalant answers

### 2015-03-07 tex-inputs/collapsed.tex
tweaked abstract and intro, cleaned up tables and added appendix sections
Fix multiply defined label, and caption for the tables showing VUR rates for all data types (in appendix)
appendix formatting
Done!
final version

@@

\begin{tabular}{| l | r | r | r | r | r |}

@@

17 & video of you at home & 81.05 & 0.60 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookvideosofyou(withaninward-facingcamera)athomecombined} \\ 
18 & photo of you intoxicated & 78.95 & 0.82 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookaphotoofyouintoxicatedcombined} \\ 
19 & photo of you at random & 78.76 & 0.85 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookphotosofyou(withaninward-facingcamera)atrandomcombined} \\ 
20 & audio recording of conversations & 78.13 & 0.83 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/recordedyourpassingconversationscombined} \\ 
21 & medical conditions & 77.7 & 0.86 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhatmedicalconditionsyouhavecombined} \\ 
22 & video of you at random & 76.19 & 0.59 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookvideosofyou(withaninward-facingcamera)atrandomcombined} \\ 
23 & video of you off-guard & 76.0 & 0.62 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookavideoofyouoff-guardcombined} \\ 
24 & photo of your work or workplace & 74.62 & 0.90 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookphotosatwork(withanoutward-facingcamera)combined} \\ 
25 & username for websites & 73.44 & 0.83 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyourusernameforwebsitescombined} \\ 
26 & address & 72.61 & 0.86 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyouraddresscombined} \\ 
27 & audio recording you captured & 72.55  & 0.70 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/copiedanduploadedaudiorecordingsyoumadeonyourdevicecombined} \\ 
28 & photo of you off-guard & 72.55 & 0.77 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookaphotoofyouoff-guardcombined} \\ 
29 & photo downloaded from internet & 71.81 & 0.90 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedphotosyoudownloadedfromtheinternetsavedonyourdevicecombined} \\ 
30 & photo others sent you & 71.63 & 1.03 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedphotosotherssenttoyousavedonyourdevicecombined} \\ 
31 & video others sent you & 70.59 & 0.81 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedvideosotherssentyousavedonyourdevicecombined} \\ 
32 & video of your work or workplace & 70.54 & 0.90 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookvideosatwork(withanoutward-facingcamera)combined} \\ 
33 & fingerprint & 70.12 & 0.86 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyourfingerprintsomehowcombined} \\ 
34 & when you were lying nervous or stressed & 69.74 & 0.91 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenyouwerelyingnervousorstressedcombined} \\ 
35 & audio recording of you (voice notes) & 69.59 & 0.91 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/recordedyoutalkingtoyourself(makingvoicenotes)combined} \\ 
36 & medication taken & 69.49 & 1.01 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhatmedicationyoutakecombined} \\ 
37 & videos already on device & 68.89 & 0.88 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedvideosyoutookwhicharealreadyonyourdevicecombined} \\ 
38 & photo of your signature & 68.07 & 0.84 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookapictureofyoursignaturecombined} \\ 
39 & web history & 66.44 & 1.01 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhatwebsitesyougotocombined} \\ 
40 & photos taken on device & 66.21 & 1.02 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedphotosyoutookwhicharealreadyonyourdevicecombined} \\ 
41 & home address & 65.0 & 0.97 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhereyoulivesomehowcombined} \\ 
42 & fine-grained location tracking (+/- cm) & 63.51 & 0.99 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/trackedwhereyouareveryaccurately(whereyouareinaroom)combined} \\ 
43 & photo of people at random & 61.94 & 1.06 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookphotosofpeople(withanoutward-facingcamera)atrandomcombined} \\ 
44 & video downloaded from the internet & 61.49 & 1.00 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedvideosyoudownloadedontheinternetsavedonyourdevicecombined} \\ 
45 & when you are alone & 61.27 & 0.99 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenandhowmuchyouspendtimealonecombined} \\ 
46 & location tracking (+/- m) & 61.24 & 1.08 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/trackedwhereyouare(likeaGPS)combined} \\ 
47 & videos of people at random & 61.04 & 0.95 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookvideosofpeople(withanoutward-facingcamera)atrandomcombined} \\ 
48 & where you are currently going & 60.87 & 0.97 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhereyouarecurrentlygoingcombined} \\ 
49 & recording of sound around you & 60.45 & 0.94 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/recordedthesoundaroundyoucombined} \\ 
50 & people you spend time with & 60.0 & 1.13 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhoyouwerespendingtimewithcombined} \\ 
51 & workplace address & 58.09 & 1.16 &\includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhereyouworksomehowcombined} \\ 
52 & sounds on device (notifications, etc) & 54.4 & 1.29 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/copiedanduploadedsoundssavedonyourdevice(notificationnoisesetc)combined} \\ 
53 & phone usage & 51.95 &1.22 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedhowmuchyouuseyourphonecombined} \\ 
54 & purchased products & 50.0 & 1.09 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhatproductsyoubuycombined} \\ 
55 & when you are sick or healthy & 48.17  & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenyouaresickorhealthycombined} \\ 
56 & how close you are to interacting people & 46.98 & 1.12 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedhowcloseyouaretootherpeopleyouinteractwithcombined} \\ 
57 & feelings (based on biometrics) & 46.81 & 1.31 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedhowyouwerefeelingbasedonheartratebreathingandortemperaturecombined} \\ 
58 & computer usage & 44.93 & 1.16 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedhowmuchyouuseyourcomputercombined} \\ 
59 & eating patterns & 42.86 & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenhowmuchandwhatyouareeatingcombined} \\ 
60 & name & 42.54 & 1.40 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyournamecombined} \\ 
61 & sleeping patterns & 40.56 & 1.34 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenandhowwellyouaresleepingcombined} \\ 
62 & eye patterns (for eye tracking) & 40.51 & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/scannedyoureyetolearnyoureyepatterns(foreyetracking)combined} \\ 
63 & exercise patterns & 38.66 & 1.26 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenhowandhowmuchyouexercisecombined} \\ 
64 & when you are happy or having fun & 34.75 & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenyouwerehappyorhavingfuncombined} \\ 
65 & television shows watched & 30.2 & 1.40 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhattelevisionshowsyouwatchcombined} \\ 
66 & when you are busy or interruptible & 29.5 & 1.26 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenyouarebusyorinterruptiblecombined} \\ 
67 & music on device & 28.06 & 1.43 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/copiedanduploadedmusicfromyourdevicecombined} \\ 
68 & heart rate & 27.5 & 1.40 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyourheartratecombined} \\ 
69 & age & 24.29 & 1.43 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyouragecombined} \\ 
70 & language spoken & 15.86 & 1.49 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedthelanguageyouwerespeakingcombined} \\ 
71 & gender & 15.0 & 1.46 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyourgendercombined} \\ 

@@

\caption{The 10 most and least upsetting data types, across all recipients. For the complete list of all data types across all recipients, see Appendix [?].}
\label{top10-table}

@@

>>>>

%\onecolumn
\section{Concern Factors}
\label{sec:concerns-appendix} 
We show the full, fine-grained results of our survey in this appendix. This includes how participants had ranked each technology in response to the Fischhoff-style questions, the VUR rates for all seventy-two data types, across all recipients and by recipient, and the details of the full regression models used in our analyses.

@@

\begin{tabular}{| r | l | r | r | r | r |}

@@

17 & how much debt you have & 81.12  & 0.54 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookavideoofyouintoxicatedcombined} \\ %learnedhowmuchdebtyouhavecombined
18 & video of you at home & 81.05 & 0.60 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookvideosofyou(withaninward-facingcamera)athomecombined} \\ 
19 & photo of you intoxicated & 78.95 & 0.82 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookaphotoofyouintoxicatedcombined} \\ 
20 & photo of you at random & 78.76 & 0.85 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookphotosofyou(withaninward-facingcamera)atrandomcombined} \\ 
21 & audio recording of conversations & 78.13 & 0.83 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/recordedyourpassingconversationscombined} \\ 
22 & medical conditions & 77.7 & 0.86 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhatmedicalconditionsyouhavecombined} \\ 
23 & video of you at random & 76.19 & 0.59 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookvideosofyou(withaninward-facingcamera)atrandomcombined} \\ 
24 & video of you off-guard & 76.0 & 0.62 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookavideoofyouoff-guardcombined} \\ 
25 & photo of your work or workplace & 74.62 & 0.90 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookphotosatwork(withanoutward-facingcamera)combined} \\ 
26 & username for websites & 73.44 & 0.83 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyourusernameforwebsitescombined} \\ 
27 & address & 72.61 & 0.86 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyouraddresscombined} \\ 
28 & audio recording you captured & 72.55  & 0.70 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/copiedanduploadedaudiorecordingsyoumadeonyourdevicecombined} \\ 
29 & photo of you off-guard & 72.55 & 0.77 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookaphotoofyouoff-guardcombined} \\ 
30 & photo downloaded from internet & 71.81 & 0.90 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedphotosyoudownloadedfromtheinternetsavedonyourdevicecombined} \\ 
31 & photo others sent you & 71.63 & 1.03 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedphotosotherssenttoyousavedonyourdevicecombined} \\ 
32 & video others sent you & 70.59 & 0.81 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedvideosotherssentyousavedonyourdevicecombined} \\ 
33 & video of your work or workplace & 70.54 & 0.90 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookvideosatwork(withanoutward-facingcamera)combined} \\ 
34 & fingerprint & 70.12 & 0.86 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyourfingerprintsomehowcombined} \\ 
35 & when you were lying nervous or stressed & 69.74 & 0.91 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenyouwerelyingnervousorstressedcombined} \\ 
36 & audio recording of you (voice notes) & 69.59 & 0.91 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/recordedyoutalkingtoyourself(makingvoicenotes)combined} \\ 
& vdots & & & \\

@@

\caption{VUR for all data types, across all recipients.}
\label{full-vur-table}

@@

\begin{tabular}{| r | l | r | r | r | r |}
& \vdots & & & \\
37 & medication taken & 69.49 & 1.01 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhatmedicationyoutakecombined} \\ 
38 & videos already on device & 68.89 & 0.88 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedvideosyoutookwhicharealreadyonyourdevicecombined} \\ 
39 & photo of your signature & 68.07 & 0.84 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookapictureofyoursignaturecombined} \\ 
40 & web history & 66.44 & 1.01 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhatwebsitesyougotocombined} \\ 
41 & photos taken on device & 66.21 & 1.02 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedphotosyoutookwhicharealreadyonyourdevicecombined} \\ 
42 & home address & 65.0 & 0.97 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhereyoulivesomehowcombined} \\ 
43 & fine-grained location tracking (+/- cm) & 63.51 & 0.99 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/trackedwhereyouareveryaccurately(whereyouareinaroom)combined} \\ 
44 & photo of people at random & 61.94 & 1.06 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookphotosofpeople(withanoutward-facingcamera)atrandomcombined} \\ 
45 & video downloaded from the internet & 61.49 & 1.00 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedvideosyoudownloadedontheinternetsavedonyourdevicecombined} \\ 
46 & when you are alone & 61.27 & 0.99 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenandhowmuchyouspendtimealonecombined} \\ 
47 & location tracking (+/- m) & 61.24 & 1.08 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/trackedwhereyouare(likeaGPS)combined} \\ 
48 & videos of people at random & 61.04 & 0.95 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookvideosofpeople(withanoutward-facingcamera)atrandomcombined} \\ 
49 & where you are currently going & 60.87 & 0.97 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhereyouarecurrentlygoingcombined} \\ 
50 & recording of sound around you & 60.45 & 0.94 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/recordedthesoundaroundyoucombined} \\ 
51 & people you spend time with & 60.0 & 1.13 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhoyouwerespendingtimewithcombined} \\ 
52 & workplace address & 58.09 & 1.16 &\includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhereyouworksomehowcombined} \\ 
53 & sounds on device (notifications, etc) & 54.4 & 1.29 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/copiedanduploadedsoundssavedonyourdevice(notificationnoisesetc)combined} \\ 
54 & phone usage & 51.95 &1.22 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedhowmuchyouuseyourphonecombined} \\ 
55 & purchased products & 50.0 & 1.09 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhatproductsyoubuycombined} \\ 
56 & when you are sick or healthy & 48.17  & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenyouaresickorhealthycombined} \\ 
57 & how close you are to interacting people & 46.98 & 1.12 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedhowcloseyouaretootherpeopleyouinteractwithcombined} \\ 
58 & feelings (based on biometrics) & 46.81 & 1.31 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedhowyouwerefeelingbasedonheartratebreathingandortemperaturecombined} \\ 
59 & computer usage & 44.93 & 1.16 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedhowmuchyouuseyourcomputercombined} \\ 
60 & eating patterns & 42.86 & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenhowmuchandwhatyouareeatingcombined} \\ 
61 & name & 42.54 & 1.40 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyournamecombined} \\ 
62 & sleeping patterns & 40.56 & 1.34 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenandhowwellyouaresleepingcombined} \\ 
63 & eye patterns (for eye tracking) & 40.51 & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/scannedyoureyetolearnyoureyepatterns(foreyetracking)combined} \\ 
64 & exercise patterns & 38.66 & 1.26 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenhowandhowmuchyouexercisecombined} \\ 
65 & when you are happy or having fun & 34.75 & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenyouwerehappyorhavingfuncombined} \\ 
66 & television shows watched & 30.2 & 1.40 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhattelevisionshowsyouwatchcombined} \\ 
67 & when you are busy or interruptible & 29.5 & 1.26 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenyouarebusyorinterruptiblecombined} \\ 
68 & music on device & 28.06 & 1.43 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/copiedanduploadedmusicfromyourdevicecombined} \\ 
69 & heart rate & 27.5 & 1.40 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyourheartratecombined} \\ 
70 & age & 24.29 & 1.43 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyouragecombined} \\ 
71 & language spoken & 15.86 & 1.49 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedthelanguageyouwerespeakingcombined} \\ 
72 & gender & 15.0 & 1.46 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyourgendercombined} \\ 
\caption{VUR for all data types, across all recipients.}
\label{full-vur-table}

### 2015-03-07 tex-inputs/results-techrank.tex
final version

We asked participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their risks and benefits. We also asked them to do this for technologies with which they were likely to be more familiar (e.g., smartphones and laptops) in addition to two examples of specific wearable devices, Google Glass and the fictitious Cubetastic3000. To calibrate our results, we also asked about four well-established technologies studied by Fischhoff \etal\cite{Fischhoff}. We found that participants generally rated technologies related to wearables as being low-risk comparatively to other technologies (Figure \ref{fig:techplot}). Appendix ~\ref{sec:riskben-appendix} shows participants' median, quartiles, and distributions of risks and benefit ratings for all technologies. We found that the calibration technologies, which were more familiar to the participants, were all rated as the most risky.

>>>>

We asked participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their risks and benefits. We also asked them to do this for technologies with which they were likely to be more familiar (e.g., smartphones and laptops) in addition to two examples of specific wearable devices, Google Glass and the fictitious Cubetastic3000. To calibrate our results, we also asked about four well-established technologies studied by Fischhoff \etal\cite{Fischhoff}. We found that participants generally rated technologies related to wearables as being low-risk comparatively to other technologies (Figure \ref{fig:techplot}). Tables \ref{risk} and \ref{benefit} in Appendix ~\ref{sec:concerns-appendix} shows participants' median, quartiles, and distributions of risks and benefit ratings for all technologies. We found that the calibration technologies, which were more familiar to the participants, were all rated as the most risky.

### 2015-03-07 tex-inputs/results-type.tex
final version

Based on our statistical models (later reported in Section \ref{sec:regression}), we observed that the largest effect on participants' VURs stemmed from the type of data being shared; data recipient and device type had weaker impacts on overall VURs. The most and least concerning data types are listed in Table \ref{top10-table}, and the full list of data can be seen in Appendix \ref{sec:data-appendix}.

>>>>

Based on our statistical models (later reported in Section \ref{sec:regression}), we observed that the largest effect on participants' VURs stemmed from the type of data being shared; data recipient and device type had weaker impacts on overall VURs. The most and least concerning data types are listed in Table \ref{top10-table}, and the full list can be seen in Table \ref{full-vur-table} in Appendix \ref{sec:concerns-appendix}.
